Naming Anonymous JavaScript Functions

### 2011-04-13 papers/splash-wavefront2011/sigplanconf-template.tex
table 6 is updated.

\begin{table*}[tb]
\centering
\scalebox{1}{
\begin{tabular}{|l|l|}
\hline
Example Code & Static Function-Object Consumption Full Name \\
\hline
Sec.~\ref{sec:arrayLiteral} outer & YUI.add(event-focus)/\_attach \\
\hline
Sec.~\ref{sec:arrayLiteral} inner & YUI.add(event-focus)/\_attach/Event.\_attach() \\
\hline
Sec.~\ref{sec:propid} & eventPool\_.createObject \\
\hline
Fig.~\ref{fig:jQueryEach} outer & jQuery.each(ajaxStart) \\
\hline
Fig.~\ref{fig:jQueryEach} inner & jQuery.each(ajaxStart)/jQuery.fn[o] \\
\hline
Sec.~\ref{sec:propexpressions}  & define/viewport[get+D] \\
\hline
Fig.~\ref{fig:classnamemanager} outer & YUI.add(classnamemanager)/Y.ClassNameManager\textless \\
\hline
Fig.~\ref{fig:classnamemanager} inner & YUI.add(classnamemanager)/Y.ClassNameManager.getClassName\textless \\
\hline
Sec.~\ref{sec:funcprop} inner & setVisible/cb\textless\\
\hline
Fig.~\ref{fig:registerWin} inner & registerWin/ \\
\hline
\end{tabular}
}
\label{table:examples}
\caption{Results from applying the approach in Sec.~\ref{sec:foc} to the examples in the paper at the point given in the first column.
Full names are listed, even in cases where our example code omitted the enclosing function scope.}
\end{table*}

@@

@@

\bibitem{FAO}
Firefox Add-ons.
\newblock https://addons.mozilla.org/en-US/developers/docs/gett ing-started.

>>>>

@@

\begin{table}[htb]
\centering
\scalebox{.8}{
{\small
\begin{tabular}{|l|l|}
\hline
Example Code & Static Function-Object Consumption Full Name \\
\hline
Sec.~\ref{sec:arrayLiteral} outer & YUI.add(event-focus)/\_attach \\
\hline
Sec.~\ref{sec:arrayLiteral}  inner & YUI.add(event-focus)/\_attach/Event.\_attach() \\
\hline
Sec.~\ref{sec:propid} & eventPool\_.createObject \\
\hline
Fig.~\ref{fig:jQueryEach} outer & jQuery.each(ajaxStart) \\
\hline
Fig.~\ref{fig:jQueryEach} inner & jQuery.each(ajaxStart)/jQuery.fn[o] \\
\hline
Sec.~\ref{sec:propexpressions}  & define/viewport[get+D] \\
\hline
Fig.~\ref{fig:classnamemanager}  outer & YUI.add(classnamem)/Y.ClassNameManager\textless \\
\hline
Fig.~\ref{fig:classnamemanager}  inner &  YUI.add(classnamem)/Y.ClassNameManager.getClassName\textless \\
\hline
Sec.~\ref{sec:funcprop}  inner & setVisible/cb\textless\\
\hline
Fig.~\ref{fig:registerWin}  inner & registerWin/ \\
\hline
\end{tabular}
}
}
\label{table:examples}
\caption{Results from applying the approach in Sec.~\ref{sec:foc} to the examples in the paper at the point given in the first column.
Full names are listed, even in cases where our example code omitted the enclosing function scope.}
\end{table}

@@

\bibitem{FAO}
Firefox Add-ons.
\newblock https://addons.mozilla.org/en-US/developers/docs/getting-started.
